Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-06-11 document/ms.tex
Addressing #13

\item {\bf Known observational uncertainties}\quad
To apply the importance sampling approximation to the published catalog, we
assume that the measurement uncertainties are known and, in this case,
Gaussian.
The assumption of normally distributed uncertainties could be relaxed given
a sampling representation of the posterior probability function for the
physical parameters (period, radius, \etc).
It is also possible to relax the noise model---to include effects like the
underestimation of uncertainties---but inference would be substantially more
computationally expensive.

@@

>>>>

\item {\bf Known observational uncertainties}\quad
To apply the importance sampling approximation to the published catalog, we
assume that the measurement uncertainties are known and, in this case,
Gaussian.
The assumption of normally distributed uncertainties could be relaxed given
a sampling representation of the posterior probability function for the
physical parameters (period, radius, \etc).
There is recent evidence that the stellar radii of \kepler\ targets might, on
average, be underestimated (\citealt{bastien}), introducing another source of
noise.
It is possible to relax the noise model and include effects like this but
inference would be substantially more computationally expensive.

@@

\bibitem[Bastien \etal(2014)]{bastien}
Bastien, F.~A., Stassun, K.~G., \& Pepper, J.\ 2014, \apjl, 788, L9
(\arxiv{1405.0940})
